Untitled

### 2020-12-07 Rcode/For_Clark_Median.Rmd

library(raster)
library(rgdal)
library(exactextractr)
library(readr)
library(plyr)
library(purrr)
```

@@

empty_list[[j]]<-exact_extract(all, poly, 'mean') #intersects boundary

@@

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out)) #take mean of the assign list above

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change 94 and 100 based on the length of your filepaths - this selects just the year and month i.e. 20041008
  colnames(out_mean)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_mean, newname, row.names = FALSE) #save as csv

@@

final_means<-list_dates %>%
  map(read_csv) %>%
  reduce(cbind)

#append park code
final_means<-data.frame(park=park_codes, final_means)

#save
write.csv(final_means, "/Users/killion/final_means2.csv", row.names = FALSE)

>>>>

library(raster)
library(rgdal)
library(exactextractr)
library(readr)
library(plyr)
library(purrr)
library(matrixStats)
```

@@

#mean of all pixels in park for each day
empty_list[[j]]<-exact_extract(all, poly, 'mean') #intersects boundary

@@

out<-as.data.frame(empty_list)
out_median<-as.data.frame(rowMedians(as.matrix(out))) #median of mean day value

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change 94 and 100 based on the length of your filepaths - this selects just the year and month i.e. 20041008
  colnames(out_median)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_median, newname, row.names = FALSE) #save as csv

@@

final_medians<-list_dates %>%
  map(read_csv) %>%
  reduce(cbind)

#append park code
final_medians<-data.frame(park=park_codes, final_medians)

#save
write.csv(final_medians, "/Users/killion/final_medians2.csv", row.names = FALSE)

### 2020-12-07 Rcode/Validation_code.Rmd

---
title: "For_Clark"
author: "Alex Killion"
date: "7/16/2020"
output: html_document
---

Packages
```{r}
library(ncdf4)
library(chron)
library(lattice)
library(RColorBrewer)

library(raster)
library(rgdal)
library(exactextractr)
library(readr)
library(plyr)
library(purrr)
```

@@

Mean in Parks w/ New Data
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}

@@

fileNames<-list.files("/Users/killion/Documents/GitHub/SmokeProject/MERRA_DATA_ORG_PRACT",full.names = TRUE)

years<-c(1980,2004)  #all the years
months<-c("01","10") #all the months
comb<-expand.grid(years,months) #just to get the number of unique combinations
list_all<-list() #create an empty list to fill with the file names

for (i in 1:nrow(comb)){ #creates the number of list objects
  year<-comb[i,]$Var1
  month<-comb[i,]$Var2
      x<-(paste0(year,month))
      list_all[[i]]<-fileNames[grep(x,fileNames)]  #fill the list with the file names
      names(list_all)[i]<-paste0("x",year,month) #name the list objects
}

list_all<- list_all[c(1,4)] #You don't need this for final run with all data

@@

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out)) #take mean of the assign list above

>>>>

---
title: "Untitled"
author: "Alex Killion"
date: "7/20/2020"
output: html_document
---

@@

```{r}

@@

list_all<- list.files("/Users/killion/Downloads/Random_Month",full.names = TRUE)

@@

out<-as.data.frame(empty_list)
out_mean_random<-as.data.frame(rowMeans(out, na.rm=TRUE)) #take mean of the assign list above
